---
title: "Checking rcartocolor for colorblind friendly palettes"
author: "Jakub Nowosad"
date: "`r Sys.Date()`"
output: 
  rmarkdown::html_vignette:
      toc: true
number_sections: true
vignette: >
  %\VignetteIndexEntry{check_rcartocolor}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.width = 6,
  fig.height = 5
)
```

```{r setup}
library(colorblindcheck)
library(rcartocolor)
```

# Quantitative

```{r}
display_carto_all(type = "quantitative")
```

## Colorblind friendly palettes

### TealGrn

```{r}
TealGrn = carto_pal(7, "TealGrn")
colorblindcheck::palette_check(TealGrn, plot = TRUE)
```

### Teal

```{r}
Teal = carto_pal(7, "Teal")
colorblindcheck::palette_check(Teal, plot = TRUE)
```

### SunsetDark

```{r}
SunsetDark = carto_pal(7, "SunsetDark")
colorblindcheck::palette_check(SunsetDark, plot = TRUE)
```

### Sunset

```{r}
Sunset = carto_pal(7, "Sunset")
colorblindcheck::palette_check(Sunset, plot = TRUE)
```

### RedOr

```{r}
RedOr = carto_pal(7, "RedOr")
colorblindcheck::palette_check(RedOr, plot = TRUE)
```

### PurpOr

```{r}
PurpOr = carto_pal(7, "PurpOr")
colorblindcheck::palette_check(PurpOr, plot = TRUE)
```

### Purp

```{r}
Purp = carto_pal(7, "Purp")
colorblindcheck::palette_check(Purp, plot = TRUE)
```

### PinkYl

```{r}
PinkYl = carto_pal(7, "PinkYl")
colorblindcheck::palette_check(PinkYl, plot = TRUE)
```

### Peach

```{r}
Peach = carto_pal(7, "Peach")
colorblindcheck::palette_check(Peach, plot = TRUE)
```

### OrYel

```{r}
OrYel = carto_pal(7, "OrYel")
colorblindcheck::palette_check(OrYel, plot = TRUE)
```

### Mint

```{r}
Mint = carto_pal(7, "Mint")
colorblindcheck::palette_check(Mint, plot = TRUE)
```

### Magenta

```{r}
Magenta = carto_pal(7, "Magenta")
colorblindcheck::palette_check(Magenta, plot = TRUE)
```

### Emrld

```{r}
Emrld = carto_pal(7, "Emrld")
colorblindcheck::palette_check(Emrld, plot = TRUE)
```

### DarkMint

```{r}
DarkMint = carto_pal(7, "DarkMint")
colorblindcheck::palette_check(DarkMint, plot = TRUE)
```

### BurgYl

```{r}
BurgYl = carto_pal(7, "BurgYl")
colorblindcheck::palette_check(BurgYl, plot = TRUE)
```

### Burg

```{r}
Burg = carto_pal(7, "Burg")
colorblindcheck::palette_check(Burg, plot = TRUE)
```

### BrwnYl

```{r}
BrwnYl = carto_pal(7, "BrwnYl")
colorblindcheck::palette_check(BrwnYl, plot = TRUE)
```

### BluYl

```{r}
BluYl = carto_pal(7, "BluYl")
colorblindcheck::palette_check(BluYl, plot = TRUE)
```

### BluGrn

```{r}
BluGrn = carto_pal(7, "BluGrn")
colorblindcheck::palette_check(BluGrn, plot = TRUE)
```

# Diverging

```{r}
display_carto_all(type = "diverging")
```

## Colorblind friendly palettes

### Earth

```{r}
Tropic = carto_pal(7, "Earth")
colorblindcheck::palette_check(Tropic, plot = TRUE)
```

### ArmyRose

```{r}
Tropic = carto_pal(7, "ArmyRose")
colorblindcheck::palette_check(Tropic, plot = TRUE)
```

### Geyser

```{r}
Tropic = carto_pal(7, "Geyser")
colorblindcheck::palette_check(Tropic, plot = TRUE)
```

## Other

### Tropic

```{r}
Tropic = carto_pal(7, "Tropic")
colorblindcheck::palette_check(Tropic, plot = TRUE)
```

### Temps

```{r}
Tropic = carto_pal(7, "Temps")
colorblindcheck::palette_check(Tropic, plot = TRUE)
```

### TealRose

```{r}
Tropic = carto_pal(7, "TealRose")
colorblindcheck::palette_check(Tropic, plot = TRUE)
```


### Fall

```{r}
Tropic = carto_pal(7, "Fall")
colorblindcheck::palette_check(Tropic, plot = TRUE)
```

# Qualitative

```{r}
display_carto_all(type = "qualitative")
```

## Colorblind friendly palettes

### Safe

```{r}
Safe = carto_pal(7, "Safe")
colorblindcheck::palette_check(Safe, plot = TRUE)
```

## Other

### Vivid

```{r}
Vivid = carto_pal(7, "Vivid")
colorblindcheck::palette_check(Vivid, plot = TRUE)
```

### Prism

```{r}
Prism = carto_pal(7, "Prism")
colorblindcheck::palette_check(Prism, plot = TRUE)
```

### Pastel

```{r}
Pastel = carto_pal(7, "Pastel")
colorblindcheck::palette_check(Pastel, plot = TRUE)
```

### Bold

```{r}
Bold = carto_pal(7, "Bold")
colorblindcheck::palette_check(Bold, plot = TRUE)
```

### Antique

```{r}
Antique = carto_pal(7, "Antique")
colorblindcheck::palette_check(Antique, plot = TRUE)
```

# Aggregation

```{r}
display_carto_all(type = "aggregation")
```

## Colorblind friendly palettes

### ag_Sunset

```{r}
ag_Sunset = carto_pal(7, "ag_Sunset")
colorblindcheck::palette_check(ag_Sunset, plot = TRUE)
```

### ag_GrnYl

```{r}
ag_GrnYl = carto_pal(7, "ag_GrnYl")
colorblindcheck::palette_check(ag_GrnYl, plot = TRUE)
```
